% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Zhicheng Lei}
\address{10 Xitucheng Road, Haidian Dist}{Beijing}{China 100876}
% \contact{
%   \phone{(+86)18501969152} \textperiodcentered\
%   \email{withlzc@gmail.com}
%   % \github[withlzc]{https://github.com/withlzc}
%   % \linkedin[billryan8]{https://www.linkedin.com/in/billryan8}
% }
\contact{(+86)18501969152}{withlzc@gmail.com}
\basicInfo{Date of Birth: Oct 10, 1996}{Nationality: Chinese}{Gender: Male}


\section{Profile}
\begin{itemize}
  \item M.S. in Software Engineering, B.S. in Information and Computing Science
  \item Excellent software development capabilities and powerful back-end engineering capabilities
  \item Good at communicating and cooperating with others
  % \item Strong programming skills with golang, java and python
\end{itemize}


% \section{\faGraduationCap\ Education}
\section{Education}
\datedsubsection{\textbf{Beijing University of Posts and Telecommunications}, Beijing, China}{Sep. 2018 -- Present}
\textit{M.S.} in Software Engineering
\\Core Modules: Network Software Design, Software Testing Technology, Design and Develop of Database Systems, Requirements Engineering, Data Warehouse and Knowledge Discovery
\datedsubsection{\textbf{Xi'an Polytechnic University}, Xi'an, China}{Sep. 2014 -- Jul. 2018}
\textit{B.S.} in Information and Computing Science
\\Core Modules: Advanced Language Programming, Data Structures and Algorithms, C++ Programming, Java and Object-Oriented Programming, Computer Networks, Database Principle and Application

\section{Work Experience}
% \datedsubsection{\textbf{FLAG Inc.} California, America}{2012 -- Present}
% \role{Summer Intern}{Manager: xxx}
% Brief introduction: xxx.
% \begin{itemize}
%   \item Implemented xxx feature
%   \item Optimized xxx 5\%
%   \item xxx
% \end{itemize}

\datedsubsection{\textbf{Lynxi Technology} Beijing, China}{Sep. 2019 -- Present}
\role{Internship}{Software Developmennt Engineer (Golang)}
Develop and maintain a back end part of the intelligent video surveillance system based on golang
\begin{itemize}
  \item Developed system business log middleware feature
  \item Refactoring program code, optimized system logic and execution efficiency
  \item Developing load balancing and scheduling modules
  \item Learning to optimized system deployment process by docker
\end{itemize}

\section{Project Experience}
% \datedsubsection{\textbf{Search Engine Projects}}{May. 2019 -- Jun. 2019}
% \role{Python, Django, ElasticSearch}{Individual Projects, collaborated with xxx}
% Brief introduction: xxx
% \begin{itemize}
%   \item Implemented xxx feature
%   \item Optimized xxx 5\%
%   \item xxx
% \end{itemize}

\datedsubsection{\textbf{Simple Blog System}}{Jul. 2019 -- Aug. 2019}
\role{Java, SpringBoot, vue.js}{}
A simple blog system based on spring boot and vue.js
\begin{itemize}
  \item Implemented back end article management, category management and tag management features
  \item Implemented front end blog display pages and blog management pages 
\end{itemize}

\datedsubsection{\textbf{Search Engine for BYRBBS}}{May. 2019 -- Jun. 2019}
\role{Python, Django, ElasticSearch}{}
Global search engine for all posts in the BYRBBS.
\begin{itemize}
  \item Crawl all post information in the forum by the Scrapy framework
  \item Save data to ElasticSearch, build the index
  \item Back end uses the Diango framework to search from ElasticSearch and interact with the front end
\end{itemize}

% \section{Skills}
% \begin{itemize}[parsep=0.5ex]
%   \item Programming Languages: Go, Java, C++, C, Python, Shell
%   \item Platform: Linux
%   \item Tools: SQL, Git, Docker
%   % \item Frameworks: Spring, Django
% \end{itemize}

% \section{\faHeartO\ Honors and Awards}
% \datedline{The Second Prize Scholarship}{May. 2017}
% \datedline{Outstanding Graduates}{Jun. 2018}

\section{Additional Skills}
\begin{itemize}[parsep=0.5ex]
  % \item Blog: \href{https://leizhicheng.com}{https://leizhicheng.com}
  % \item GitHub: \href{https://github.com/withlzc}{https://github.com/withlzc}
  \item IT Skills: Golang, Java, C++, C, Python, Shell, SQL, Redis, Git, Docker
  \item Languages: English - Fluent, Chinese - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
